---
title: "Testing"
author: "Andrew Heiss"
mainfont: Clear Sans
fontsize: 10pt
output:
  pdf_document:
    includes:
      in_header: ../TeX/top_stuff.tex
    latex_engine: xelatex
    toc: yes
    toc_depth: 1
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Set the working directory one level back
library(knitr)
opts_knit$set(root.dir = normalizePath('../'))

library(pander)
panderOptions('table.split.table', Inf)
# panderOptions('knitr.auto.asis', FALSE)  # Someday

# Process and clean all the data
source("../R/clean_data.R", chdir=TRUE)

# Load plotting helper functions
source("../R/summary_functions.R", chdir=TRUE)

```


# Q1.2: What is the name of your organization?

```{r, echo=FALSE, results='asis'}
# if (metadata$hide.anonymous == TRUE) {
#   org.names <- responses.org.foreign %>% filter(Q1.3 == "No") %>% select(name = Q1.2)
# } else {
  org.names <- responses.org.foreign %>% select(name = Q1.2)
# }
pandoc.list(text.list(org.names$name))
```


# Q1.3: Would you like your organization to remain anonymous in this study's reports?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
# Q1.3: Would you like your organization to remain anonymous in this study's reports?
plot.single.question(responses.org.foreign$Q1.3)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(factor.summary(responses.org.foreign$Q1.3))
```


# Q1.4: Where is your organization's main office?


# Q1.5: In how many countries has your organization done most of its advocacy work over the past 10 years?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
plot.single.question(responses.org.foreign$Q1.5)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(numeric.summary(responses.org.foreign$Q1.5))
```


# Q2.1: About what percent of your organization's time and resources are spent on fighting against trafficking or helping victims of trafficking?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
ggplot(responses.org.foreign, aes(x=Q2.1/100)) + 
  geom_histogram(binwidth=.1, fill=bar.color.single) + 
  labs(x=NULL, y="Proportion") + scale_x_continuous(labels = percent) +
  theme_bar
```

```{r, echo=FALSE, results='asis'}
pandoc.table(numeric.summary(responses.org.foreign$Q2.1))
```


# Q2.2: Which human trafficking issues is your organization most involved with?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
cols <- c("Q2.2_1", "Q2.2_2", "Q2.2_3", "Q2.2_4")
labels <- c("Organ trafficking", "Sex trafficking", 
            "Labor trafficking", "Other")

plot.multiple.answers(cols, labels)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(separate.answers.summary(responses.org.foreign, cols, 
                                      labels, n=num.responses, total=TRUE))
```

## Other responses

```{r, echo=FALSE, results='asis'}
pandoc.list(text.list(responses.org.foreign$Q2.2_4_TEXT))
```


# Q2.3: Which kinds of victims is your organization most involved with?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
cols <- c("Q2.3_1", "Q2.3_2", "Q2.3_3")
labels <- c("Children", "Adults", "Other")

plot.multiple.answers(cols, labels)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(separate.answers.summary(responses.org.foreign, cols, 
                                      labels, n=num.responses, total=TRUE))
```

## Other responses

```{r, echo=FALSE, results='asis'}
pandoc.list(text.list(responses.org.foreign$Q2.3_3_TEXT))
```


# Q2.4: Which efforts does your organization focus on most?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
cols <- c("Q2.4_1", "Q2.4_2", "Q2.4_3", "Q2.4_4", "Q2.4_5")
labels <- c("Prevention and education", "Prosecutions and legal issues",
            "Victim protection", "Victim assistance", "Other")

plot.multiple.answers(cols, labels, flipped=TRUE)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(separate.answers.summary(responses.org.foreign, cols, 
                                      labels, n=num.responses, total=TRUE))
```

## Other responses

```{r, echo=FALSE, results='asis'}
pandoc.list(text.list(responses.org.foreign$Q2.4_5_TEXT))
```


# Q2.5: The US State Department issues an annual Trafficking in Persons (TIP) report. Have you ever heard of this annual report?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
plot.single.question(responses.org.foreign$Q2.5)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(factor.summary(responses.org.foreign$Q2.5))
```


# Q2.6: In Fall 2013 an NGO named WalkFree published a "Human Trafficking Index" that rated countries on how many trafficking victims they have. Have you heard of this index?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
plot.single.question(responses.org.foreign$Q2.6)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(factor.summary(responses.org.foreign$Q2.6))
```



# Q3.2: Where has your organization done advocacy work?


# Q3.2a: Countries that have no reported advocacy work


# Q3.3: How much does your organization know about human trafficking policy in X?

```{r, warning=FALSE, echo=FALSE, fig.width=6.5, fig.height=3}
plot.single.question(responses.countries$Q3.3)
```

```{r, echo=FALSE, results='asis'}
pandoc.table(factor.summary(responses.countries$Q3.3))
```

